---
title: "Experiment of DriveML R package - Big Data set"
author: "Dayanand, Sayan, Ravi, Kiran R"
date: "16/06/2021"
output: html_document
---

```{r setup0, include=TRUE,eval=FALSE, warning=FALSE}
library(DriveML)    ## automl package
library(data.table) ## data wrangling package
library(caret)      ## ML wrapper package
library(mlr)        ## ML wrapper package
library(h2o)        ## automl package
library(OneR)       ## automl package
library(Metrics)    ## auc function
library(autoxgboost)## automl package
```

```{r setup, include=FALSE, eval=TRUE, warning=FALSE}
library(DriveML)    ## automl package
library(data.table) ## data wrangling package
library(caret)      ## ML wrapper package
library(mlr)        ## ML wrapper package
library(h2o)        ## automl package
library(OneR)       ## automl package
library(Metrics)    ## auc function
library(autoxgboost)## automl package
```

## Rain in Australia

data source : **https://www.kaggle.com/jsphyg/weather-dataset-rattle-package**

#### Content

`This dataset contains about 10 years of daily weather observations from many locations across Australia.

RainTomorrow is the target variable to predict. It means -- did it rain the next day, Yes or No? This column is Yes if the rain for that day was 1mm or more.`

##### Problem Statement

Predict next-day rain by training classification models on the target variable RainTomorrow

###### Source & Acknowledgements
Observations were drawn from numerous weather stations. The daily observations are available from **http://www.bom.gov.au/climate/data.**
An example of latest weather observations in Canberra: **http://www.bom.gov.au/climate/dwo/IDCJDW2801.latest.shtml**

Definitions adapted from **http://www.bom.gov.au/climate/dwo/IDCJDW0000.shtml**
Data source: **http://www.bom.gov.au/climate/dwo/ and http://www.bom.gov.au/climate/data.**

Copyright Commonwealth of Australia 2010, Bureau of Meteorology.
