---
title: "Experiment of DriveML R package - Small Data set"
author: "Dayanand, Sayan, Ravi, Kiran R"
date: "16/06/2021"
output: html_document
---

```{r setup0, include=TRUE,eval=FALSE, warning=FALSE}
library(DriveML)    ## automl package
library(data.table) ## data wrangling package
library(caret)      ## ML wrapper package
library(mlr)        ## ML wrapper package
library(h2o)        ## automl package
library(OneR)       ## automl package
library(Metrics)    ## auc function
library(autoxgboost)## automl package
```

```{r setup, include=FALSE, eval=TRUE, warning=FALSE}
library(DriveML)    ## automl package
library(data.table) ## data wrangling package
library(caret)      ## ML wrapper package
library(mlr)        ## ML wrapper package
library(h2o)        ## automl package
library(OneR)       ## automl package
library(Metrics)    ## auc function
library(autoxgboost)## automl package
```

## Heart Disease UCI

data source : **https://archive.ics.uci.edu/ml/datasets/Heart+Disease**

#### Content

This database contains 76 attributes, but all published experiments refer to using a subset of 14 of them. In particular, the Cleveland database is the only one that has been used by ML researchers to
this date. The "goal" field refers to the presence of heart disease in the patient. It is integer valued from 0 (no presence) to 4.


**Acknowledgements:**

Creators:

Hungarian Institute of Cardiology. Budapest: Andras Janosi, M.D.
University Hospital, Zurich, Switzerland: William Steinbrunn, M.D.
University Hospital, Basel, Switzerland: Matthias Pfisterer, M.D.
V.A. Medical Center, Long Beach and Cleveland Clinic Foundation: Robert Detrano, M.D., Ph.D.
Donor:
David W. Aha (aha '@' ics.uci.edu) (714) 856-8779


