---
title: "Experiment of DriveML R package - Large Data set"
author: "Dayanand, Sayan, Ravi, Kiran R"
date: "16/06/2021"
output: html_document
---

```{r setup0, include=TRUE,eval=FALSE, warning=FALSE}
library(DriveML)    ## automl package
library(data.table) ## data wrangling package
library(caret)      ## ML wrapper package
library(mlr)        ## ML wrapper package
library(h2o)        ## automl package
library(OneR)       ## automl package
library(Metrics)    ## auc function
library(autoxgboost)## automl package
```

```{r setup, include=FALSE, eval=TRUE, warning=FALSE}
library(DriveML)    ## automl package
library(data.table) ## data wrangling package
library(caret)      ## ML wrapper package
library(mlr)        ## ML wrapper package
library(h2o)        ## automl package
library(OneR)       ## automl package
library(Metrics)    ## auc function
library(autoxgboost)## automl package
```

## Adult Data Set

data source : **https://archive.ics.uci.edu/ml/datasets/adult**

#### Content

Extraction was done by Barry Becker from the 1994 Census database. A set of reasonably clean records was extracted using the following conditions: ((AAGE>16) && (AGI>100) && (AFNLWGT>1)&& (HRSWK>0))

Prediction task is to determine whether a person makes over 50K a year.

**Source:**

Donor:

Ronny Kohavi and Barry Becker
Data Mining and Visualization
Silicon Graphics.
e-mail: ronnyk '@' live.com for questions.

##### Problem Statement

Predict whether income exceeds $50K/yr based on census data. Also known as "Census Income" dataset.

